---
title: "Preregistration Data Donation Template"
format:
  docx:
    toc: true
    toc-depth: 2
    number-sections: false
  pdf:
    toc: true
    toc-depth: 2
    number-sections: false
    colorlinks: true
    geometry:
      - margin=1in
    fontsize: 11pt
    documentclass: article
    papersize: a4
params:
  # METADATA
  title: ""
  authors: ""
  date: ""
  license: ""
  ethics: ""
  foreknowledge: ""
  foreknowledge_explanation: ""

  # RESEARCH QUESTIONS & HYPOTHESES
  background: ""
  research_questions: ""

  # GENERAL STUDY DESIGN
  study_type_general: ""
  study_type_other: ""
  researcher_workflow: ""
  user_workflow: ""
  experimental_conditions: ""
  blinding_experiment: ""
  randomization_general: ""
  informed_consent: ""

  # SAMPLING PLAN
  population: ""
  sample_size: ""
  platform_population: ""
  platform_sample_size: ""
  observation_period: ""
  representation_errors: ""

  # MEASURES: DATA DONATION
  raw_data_donation: ""
  collected_variables: ""
  new_variables: ""
  quality_control: ""
  measurement_error_reflections: ""
  other_information: ""

  # MEASURES: OTHER DATA
  quantitative_variables_collected: ""
  qualitative_variables: ""
  additional_other_information: ""

  # ANALYSIS PLAN
  data_cleaning: ""
  analysis_plan: ""
  inference_criteria: ""

  # REFERENCES
  references: ""

  # UPLOADED FILE NAMES (recorded as attachments)
  data_documentation_file: ""
  stimuli_file: ""
  user_instructions_file: ""
  other_information_file: ""
  additional_other_information_file: ""
  additional_material_file: ""
---

```{r}
#| include: false

# Print a parameter value as flowing text. Empty/NULL values render as a
# light placeholder so reviewers can see the field was left blank rather than
# a section silently disappearing. Multi-line inputs (repeatable blocks join
# their entries with blank lines) are split into separate paragraphs.
render_text <- function(x) {
  if (is.null(x) || length(x) == 0 || all(trimws(x) == "")) {
    cat("*(not specified)*")
    return(invisible())
  }
  # Split on blank lines into paragraphs; keep single newlines as soft breaks.
  paras <- strsplit(x, "\n[[:space:]]*\n")[[1]]
  paras <- paras[trimws(paras) != ""]
  cat(paste(trimws(paras), collapse = "\n\n"))
}

# Record an uploaded file, if one was provided.
render_file <- function(x) {
  if (is.null(x) || length(x) == 0 || all(trimws(x) == "")) {
    cat("*(no file uploaded)*")
    return(invisible())
  }
  cat("Attached file: ", trimws(x), sep = "")
}
```

# Metadata

## Title

```{r}
#| echo: false
#| output: asis
render_text(params$title)
```

## Authors & Affiliations

```{r}
#| echo: false
#| output: asis
render_text(params$authors)
```

## Date of Preregistration

```{r}
#| echo: false
#| output: asis
d <- suppressWarnings(as.Date(params$date))
if (is.null(params$date) || is.na(d)) {
  cat("*(not specified)*")
} else {
  cat(format(d, "%B %d, %Y"))
}
```

## License

```{r}
#| echo: false
#| output: asis
render_text(params$license)
```

## Ethics Approval / IRB Status

```{r}
#| echo: false
#| output: asis
render_text(params$ethics)
```

## Status of Study (Foreknowledge of Data or Evidence)

```{r}
#| echo: false
#| output: asis
render_text(params$foreknowledge)
```

## Explanation of Data Foreknowledge

```{r}
#| echo: false
#| output: asis
render_text(params$foreknowledge_explanation)
```

{{< pagebreak >}}

# Research Questions & Hypotheses

## Background & Rationale

```{r}
#| echo: false
#| output: asis
render_text(params$background)
```

## Research Questions or Hypotheses

```{r}
#| echo: false
#| output: asis
render_text(params$research_questions)
```

{{< pagebreak >}}

# General Study Design

## Study Type

```{r}
#| echo: false
#| output: asis
render_text(params$study_type_general)
```

## Description of Study Type

```{r}
#| echo: false
#| output: asis
render_text(params$study_type_other)
```

## Researcher-Side Workflow & Tool for Data Donation

```{r}
#| echo: false
#| output: asis
render_text(params$researcher_workflow)
```

## User-Side Workflow & Data Collection Procedure

```{r}
#| echo: false
#| output: asis
render_text(params$user_workflow)
```

## Experimental Conditions

```{r}
#| echo: false
#| output: asis
render_text(params$experimental_conditions)
```

```{r}
#| echo: false
#| output: asis
render_file(params$stimuli_file)
```

## Blinding

```{r}
#| echo: false
#| output: asis
render_text(params$blinding_experiment)
```

## Randomization

```{r}
#| echo: false
#| output: asis
render_text(params$randomization_general)
```

## Informed Consent

```{r}
#| echo: false
#| output: asis
render_text(params$informed_consent)
```

```{r}
#| echo: false
#| output: asis
render_file(params$user_instructions_file)
```

{{< pagebreak >}}

# Sampling Plan

## Participants — Target Population & Sample

```{r}
#| echo: false
#| output: asis
render_text(params$population)
```

## Participants — Sample Size

```{r}
#| echo: false
#| output: asis
render_text(params$sample_size)
```

## Platforms/Devices — Target Population & Sample

```{r}
#| echo: false
#| output: asis
render_text(params$platform_population)
```

## Platforms/Devices — Sample Size

```{r}
#| echo: false
#| output: asis
render_text(params$platform_sample_size)
```

## Observation Period

```{r}
#| echo: false
#| output: asis
render_text(params$observation_period)
```

## Reflections on Errors in Representation

```{r}
#| echo: false
#| output: asis
render_text(params$representation_errors)
```

{{< pagebreak >}}

# Measures: Data Donation

## Raw Data Structure

```{r}
#| echo: false
#| output: asis
render_text(params$raw_data_donation)
```

```{r}
#| echo: false
#| output: asis
render_file(params$data_documentation_file)
```

## Collected Variables

```{r}
#| echo: false
#| output: asis
render_text(params$collected_variables)
```

## Any Other Variables Derived from the Data Donations

```{r}
#| echo: false
#| output: asis
render_text(params$new_variables)
```

## Quality Control Procedures

```{r}
#| echo: false
#| output: asis
render_text(params$quality_control)
```

## Reflections on Measurement Errors

```{r}
#| echo: false
#| output: asis
render_text(params$measurement_error_reflections)
```

## Other Information

```{r}
#| echo: false
#| output: asis
render_text(params$other_information)
```

```{r}
#| echo: false
#| output: asis
render_file(params$other_information_file)
```

{{< pagebreak >}}

# Measures: Other Data

## Variables Collected from Other Quantitative Data Collection

```{r}
#| echo: false
#| output: asis
render_text(params$quantitative_variables_collected)
```

## Variables Collected from Other Qualitative Data Collection

```{r}
#| echo: false
#| output: asis
render_text(params$qualitative_variables)
```

## Other Information

```{r}
#| echo: false
#| output: asis
render_text(params$additional_other_information)
```

```{r}
#| echo: false
#| output: asis
render_file(params$additional_other_information_file)
```

{{< pagebreak >}}

# Analysis Plan

## Data Cleaning

```{r}
#| echo: false
#| output: asis
render_text(params$data_cleaning)
```

## Analysis

```{r}
#| echo: false
#| output: asis
render_text(params$analysis_plan)
```

## Inference Criteria

```{r}
#| echo: false
#| output: asis
render_text(params$inference_criteria)
```

{{< pagebreak >}}

# References

## References

```{r}
#| echo: false
#| output: asis
render_text(params$references)
```

## Any Additional Information

```{r}
#| echo: false
#| output: asis
render_file(params$additional_material_file)
```
