---
title: "Preregistration Data Donation Template"
format:
  pdf:
    toc: true
    toc-depth: 2

    number-sections: false

    colorlinks: false

    geometry:
      - margin=1in

    fontsize: 11pt

    documentclass: scrartcl

    papersize: a4

    titlepage: true

    include-in-header:
      text: |
        \usepackage{xcolor}
        \definecolor{black}{HTML}{2B6CB0}

        \usepackage{titlesec}

        \titleformat{\section}
        {\Large\bfseries\color{black}}
        {\thesection}
        {1em}
        {}

        \titleformat{\subsection}
        {\large\bfseries}
        {}
        {0em}
        {}

        \usepackage{tcolorbox}

        \tcbset{
          colback=black!2,
          colframe=black!25,
          arc=3mm
        }
         \usepackage{etoolbox}

        \makeatletter
        \patchcmd{\tableofcontents}
          {\endgroup}
          {\endgroup\clearpage}
          {}{}
        \makeatother

  
params:
  # METADATA
  title: ""
  authors: ""
  date: ""
  version_identifier: ""
  license: ""
  keywords: ""
  funding: ""
  ethics: ""

  # STUDY OVERVIEW
  background: ""
  objectives: ""
  hypotheses: ""
  exploratory_questions: ""
  ddp_justification: ""

  # DATA SOURCES
  platform_tool: ""
  access_method: ""
  dataset_description: ""
  download_dates: ""
  availability: ""
  prior_knowledge: ""
  codebook: ""
  collection_procedures: ""
  privacy_security: ""

  # SAMPLING
  population: ""
  recruitment: ""
  sample_size: ""
  stopping_rule: ""
  representativeness: ""

  # DATA STRUCTURE
  raw_data_structure: ""
  data_cleaning: ""
  feature_extraction: ""
  assumptions: ""
  missing_data: ""

  # STUDY DESIGN
  study_type: ""
  blinding: ""
  design_description: ""
  conditions: ""
  randomization: ""

  # MEASUREMENTS
  independent_variables: ""
  dependent_variables: ""
  control_variables: ""
  derived_variables: ""
  platform_indicators: ""

  # ANALYSIS
  primary_analyses: ""
  secondary_analyses: ""
  inference_criteria: ""
  modeling_parameters: ""
  performance_measures: ""
  software_packages: ""
  reproducibility: ""

  # RISKS
  participant_risks: ""
  risk_mitigation: ""
  ethical_justification: ""

  # OPEN SCIENCE
  data_sharing: ""
  code_sharing: ""
  pipeline_documentation: ""
  update_policy: ""

  # REFERENCES
  citations: ""
  appendices: ""
---

```{r}
#| include: false

render_text <- function(x, width = 80) {

  if (is.null(x) || x == "") return(invisible())

  cat(
    strwrap(
      x,
      width = width
    ),
    sep = "\n"
  )
}
```


# Metadata:

## Title:

```{r}
#| echo: false
  render_text(params$title)
```

## Authors & Affiliations:

```{r}
#| echo: false
render_text(params$authors)
```

## Date of Preregistration:

```{r}
#| echo: false 
cat(format(as.Date(params$date), "%B %d, %Y"))
```

## Version identifier

```{r}
#| echo: false
render_text(params$version_identifier)
```

## License (choose from the OSF license list)

```{r}
#| echo: false

render_text(params$license)

```

## Keywords

```{r}
#| echo: false
render_text(params$keywords)
```

## Funding

```{r}
#| echo: false
render_text(params$funding)
```

## Ethics

```{r}
#| echo: false
render_text(params$ethics)
```

\clearpage
# Study Overview

## Background

```{r}
#| echo: false
render_text(params$background)
```

## Objectives

```{r}
#| echo: false
render_text(params$objectives)
```

## Hypotheses

```{r}
#| echo: false
render_text(params$hypotheses)
```

## Exploratory Questions

```{r}
#| echo: false
render_text(params$exploratory_questions)
```

## DDP Justification

```{r}
#| echo: false
render_text(params$ddp_justification)
```

\clearpage
# Data sources

## Platform Tools

```{r}
#| echo: false
render_text(params$platform_tool)
```

## Access Method

```{r}
#| echo: false
render_text(params$access_method)
```

## Dataset Description

```{r}
#| echo: false
render_text(params$dataset_description)
```

## Download Dates

```{r}
#| echo: false
render_text(params$download_dates)
```

## Availability

```{r}
#| echo: false
render_text(params$availability)
```

## Prior Knowledge

```{r}
#| echo: false
render_text(params$prior_knowledge)
```

## Codebook

```{r}
#| echo: false
render_text(params$codebook)
```

## Collection Procedures

```{r}
#| echo: false
render_text(params$collection_procedures)
```

## Privacy Security

```{r}
#| echo: false
render_text(params$privacy_security)
```

\clearpage
# Sampling

## Population

```{r}
#| echo: false
render_text(params$population)
```

## Recruitment

```{r}
#| echo: false
render_text(params$recruitment)
```

## Sample Size

```{r}
#| echo: false
render_text(params$sample_size)
```

## Stopping Rule

```{r}
#| echo: false
render_text(params$stopping_rule)
```

## Representativeness

```{r}
#| echo: false
render_text(params$representativeness)
```

\clearpage
# Data Structure

## Raw Data Structure

```{r}
#| echo: false
render_text(params$raw_data_structure)
```

## Data Cleaning

```{r}
#| echo: false
render_text(params$data_cleaning)
```

## Feature Extraction

```{r}
#| echo: false
render_text(params$feature_extraction)
```

## Assumptions

```{r}
#| echo: false
render_text(params$assumptions)
```

## Missing Data

```{r}
#| echo: false
render_text(params$missing_data)
```

\clearpage
# Study Design

## Study Type

```{r}
#| echo: false
render_text(params$study_type)
```

## Blinding

```{r}
#| echo: false
render_text(params$blinding)
```

## Design Description

```{r}
#| echo: false
render_text(params$design_description)
```

## Conditions

```{r}
#| echo: false
render_text(params$conditions)
```

## Randomization

```{r}
#| echo: false
render_text(params$randomization)
```

\clearpage
# Measurements

## Independent Variables

```{r}
#| echo: false
render_text(params$independent_variables)
```

## Dependent Variables

```{r}
#| echo: false
render_text(params$dependent_variables)
```

## Control Variables

```{r}
#| echo: false
render_text(params$control_variables)
```

## Derived Variables

```{r}
#| echo: false
render_text(params$derived_variables)
```

## Platform Indicators

```{r}
#| echo: false
render_text(params$platform_indicators)
```

\clearpage
# Analysis

## Primary Analyses

```{r}
#| echo: false
render_text(params$primary_analyses)
```

## Secondary Analyses

```{r}
#| echo: false
render_text(params$secondary_analyses)
```

## Inference Criteria

```{r}
#| echo: false
render_text(params$inference_criteria)
```

## Modeling Parameters

```{r}
#| echo: false
render_text(params$modeling_parameters)
```

## Performance Measures

```{r}
#| echo: false
render_text(params$performance_measures)
```

## Software Packages

```{r}
#| echo: false
render_text(params$software_packages)
```

## Reproducibility

```{r}
#| echo: false
render_text(params$reproducibility)
```

\clearpage
# Risks

## Participant Risks

```{r}
#| echo: false
render_text(params$participant_risks)
```

## Risk Mitigation

```{r}
#| echo: false
render_text(params$risk_mitigation)
```

## Ethical Justification

```{r}
#| echo: false
render_text(params$ethical_justification)
```

\clearpage
# Open Science

## Data Sharing

```{r}
#| echo: false
render_text(params$data_sharing)
```

## Code Sharing

```{r}
#| echo: false
render_text(params$code_sharing)
```

## Pipeline documentation

```{r}
#| echo: false
render_text(params$pipeline_documentation)
```

## Update Policy

```{r}
#| echo: false
render_text(params$update_policy)
```

\clearpage
# References

## Citations

```{r}
#| echo: false
render_text(params$citations)
```

## Appendices

```{r}
#| echo: false
render_text(params$appendices)
```
