---
title: "Preregistration Data Donation Template"
format:
  pdf:
    toc: false

params:
  # METADATA
  title: ""
  authors: ""
  date: ""
  version_identifier: ""
  license: ""
  keywords: ""
  funding: ""
  ethics: ""

  # STUDY OVERVIEW
  background: ""
  objectives: ""
  hypotheses: ""
  exploratory_questions: ""
  ddp_justification: ""

  # DATA SOURCES
  platform_tool: ""
  access_method: ""
  dataset_description: ""
  download_dates: ""
  availability: ""
  prior_knowledge: ""
  codebook: ""
  collection_procedures: ""
  privacy_security: ""

  # SAMPLING
  population: ""
  recruitment: ""
  sample_size: ""
  stopping_rule: ""
  representativeness: ""

  # DATA STRUCTURE
  raw_data_structure: ""
  data_cleaning: ""
  feature_extraction: ""
  assumptions: ""
  missing_data: ""

  # STUDY DESIGN
  study_type: ""
  blinding: ""
  design_description: ""
  conditions: ""
  randomization: ""

  # MEASUREMENTS
  independent_variables: ""
  dependent_variables: ""
  control_variables: ""
  derived_variables: ""
  platform_indicators: ""

  # ANALYSIS
  primary_analyses: ""
  secondary_analyses: ""
  inference_criteria: ""
  modeling_parameters: ""
  performance_measures: ""
  software_packages: ""
  reproducibility: ""

  # RISKS
  participant_risks: ""
  risk_mitigation: ""
  ethical_justification: ""

  # OPEN SCIENCE
  data_sharing: ""
  code_sharing: ""
  pipeline_documentation: ""
  update_policy: ""

  # REFERENCES
  citations: ""
  appendices: ""
---


# Metadata:

## Title:
```{r}
#| echo: false
cat(params$title)
```
## Authors & Affiliations:
```{r}
#| echo: false
cat(params$authors)
```
## Date of Preregistration:
```{r}
#| echo: false 
cat(format(as.Date(params$date), "%B %d, %Y"))
```
## Version identifier
```{r}
#| echo: false
cat(params$version_identifier)
```
## License (choose from the OSF license list)
```{r}
#| echo: false

cat(params$license)

```
## Keywords
```{r}
#| echo: false
cat(params$keywords)
```
## Funding
```{r}
#| echo: false
cat(params$funding)
```
## Ethics
```{r}
#| echo: false
cat(params$ethics)
```

# STUDY OVERVIEW
## background
```{r}
#| echo: false
cat(params$background)
```
## objectives
```{r}
#| echo: false
cat(params$objectives)
```
## hypotheses
```{r}
#| echo: false
cat(params$hypotheses)
```
## exploratory_questions
```{r}
#| echo: false
cat(params$exploratory_questions)
```
## ddp_justification
```{r}
#| echo: false
cat(params$ddp_justification)
```
 
# DATA SOURCES
## platform_tool
```{r}
#| echo: false
cat(params$platform_tool)
```
## access_method
```{r}
#| echo: false
cat(params$access_method)
```
## dataset_description
```{r}
#| echo: false
cat(params$dataset_description)
```
## download_dates
```{r}
#| echo: false
cat(params$download_dates)
```
## availability
```{r}
#| echo: false
cat(params$availability)
```
## prior_knowledge
```{r}
#| echo: false
cat(params$prior_knowledge)
```
## codebook
```{r}
#| echo: false
cat(params$codebook)
```
## collection_procedures
```{r}
#| echo: false
cat(params$collection_procedures)
```
## privacy_security
```{r}
#| echo: false
cat(params$privacy_security)
```
 
# SAMPLING
## population
```{r}
#| echo: false
cat(params$population)
```
## recruitment
```{r}
#| echo: false
cat(params$recruitment)
```
## sample_size
```{r}
#| echo: false
cat(params$sample_size)
```
## stopping_rule
```{r}
#| echo: false
cat(params$stopping_rule)
```
## representativeness
```{r}
#| echo: false
cat(params$representativeness)
```
 
# DATA STRUCTURE
## raw_data_structure
```{r}
#| echo: false
cat(params$raw_data_structure)
```
## data_cleaning
```{r}
#| echo: false
cat(params$data_cleaning)
```
## feature_extraction
```{r}
#| echo: false
cat(params$feature_extraction)
```
## assumptions
```{r}
#| echo: false
cat(params$assumptions)
```
## missing_data
```{r}
#| echo: false
cat(params$missing_data)
```
 
# STUDY DESIGN
## study_type
```{r}
#| echo: false
cat(params$study_type)
```
## blinding
```{r}
#| echo: false
cat(params$blinding)
```
## design_description
```{r}
#| echo: false
cat(params$design_description)
```
## conditions
```{r}
#| echo: false
cat(params$conditions)
```
## randomization
```{r}
#| echo: false
cat(params$randomization)
```
 
# MEASUREMENTS
## independent_variables
```{r}
#| echo: false
cat(params$independent_variables)
```
## dependent_variables
```{r}
#| echo: false
cat(params$dependent_variables)
```
## control_variables
```{r}
#| echo: false
cat(params$control_variables)
```
## derived_variables
```{r}
#| echo: false
cat(params$derived_variables)
```
## platform_indicators
```{r}
#| echo: false
cat(params$platform_indicators)
```
 
# ANALYSIS
## primary_analyses
```{r}
#| echo: false
cat(params$primary_analyses)
```
## secondary_analyses
```{r}
#| echo: false
cat(params$secondary_analyses)
```
## inference_criteria
```{r}
#| echo: false
cat(params$inference_criteria)
```
## modeling_parameters
```{r}
#| echo: false
cat(params$modeling_parameters)
```
## performance_measures
```{r}
#| echo: false
cat(params$performance_measures)
```
## software_packages
```{r}
#| echo: false
cat(params$software_packages)
```
## reproducibility
```{r}
#| echo: false
cat(params$reproducibility)
```
 
# RISKS
## participant_risks
```{r}
#| echo: false
cat(params$participant_risks)
```
## risk_mitigation
```{r}
#| echo: false
cat(params$risk_mitigation)
```
## ethical_justification
```{r}
#| echo: false
cat(params$ethical_justification)
```
 
# OPEN SCIENCE
## data_sharing
```{r}
#| echo: false
cat(params$data_sharing)
```
## code_sharing
```{r}
#| echo: false
cat(params$code_sharing)
```
## pipeline_documentation
```{r}
#| echo: false
cat(params$pipeline_documentation)
```
## update_policy
```{r}
#| echo: false
cat(params$update_policy)
```
 
# REFERENCES
## citations
```{r}
#| echo: false
cat(params$citations)
```
## appendices
```{r}
#| echo: false
cat(params$appendices)
```
